---
title: "CDOM data batches - collate the data, check for drift and apply corrections"
autput: html_document
author: "Daniel Moran"
organisation: "AIMS"
date:   "14/04/2021"
update: 20/05/2020 to include drift corrections and apply absorbant coefficient calcs to corrected data
update: 03/12/2020 to apply modeled data over a narrower range. 350-680nm. objective is to provide a better modeled fit.
update: 06/01/2021 to change scan plots with wavelgth on the x axis instead of deltaLambda. and collate CDOM443 values from modeled outputs based on the corrected data
update: 29/04/2021 review by Alex Macadam to bring up to R version 4.0.5 and RStudio version 1.4.1106 and format for RMarkdown. 
update: 07/04/2021 to include R2 value for each scan/model.
update: 17/05/2021 removed unused code and added R2 values to graph headers
update: 18/05/2021 added clear environment in line 33
update: 06/07/2021 combined modelled443 and R2 into the model443 outputs csv. moved this file to outputs/data.
update: 10/02/2023 added additional details to the upfront instructions.
update: 10/05/2023 changed the theme for the blank driftplots from "theme_minimal" to "theme_gray" due to problems we were having black plot backgrounds being output on some user laptops - not sure what the issue was but perhaps related to user settings somehow - "theme_gray" seems to have solved the problem.
update: 04/03/2025 arbitrary version update before start  of 2024-25 conversions
update: 17/06/2025 moved this script to github repo MMP-CDOM/main and renamed to remove now redundant version control (no longer required with move to github). Confirmed this script compatible with R version 4.3.1 (2023-06-16 ucrt) -- "Beagle Scouts" and RStudio 2025.05.1+513 "Mariposa Orchid" Release (ab7c1bc795c7dcff8f26215b832a3649a19fc16c, 2025-06-01) for windows.
update: 20/07/2026 adjustments for 2025-26 JCU lab data. 
update: 12/08/2026: due to a mistake in the script the model was not previously being fitted over narrower range 350-680nm (it was only being plotted over that range). I have now improved model fit by adjusting to fit the model over range 380-680nm. This has narrowed the range and also avoids instrument noise from lamp changeover (worst between 340-380nm - noise created by the end range of the tungsten (visible) lamp before the change to deuterium (UV) lamp at 340nm). Have also improved fit by refining the starting value for S during model fitting (was start=list(S=1), now start=list(S=0.015)) since the model was falling over over the reduced range du to high starting value for S. I also tried adding K factor to model (K accounts for residual scattering or baseline offsets), although this appears to provide a slight improvement to R2 the model without K provides a better representation of Acdom(443) (based on examinations using test data from batch CDOM-20251210_CYA001-005_&_CYA037-041_&_CYA049-050) so I have continued to model without K. (noting that inner filter corrections are already applied by subtracting mean absorbance 600-750 nm during conversion to Acdom)
                    - variance in modelled Acdom(443) from observed using model without K: mean = 0.00001, stdev = 0.003955274
                    - variance in modelled Acdom(443) from observed using model with K: mean = -0.001328288, stdev = 0.003211442
update: 20/08/2026: debugging and improvement to the JCU lab processing script for the 2026 update to improved model fitting and script overhaul (prior to re-run of all processing of the event data)

This script is confirmed to be compatible with R version 4.3.1 and Rstudio version 2025.05.1+513
Combine multiple .csv files from a batch of UV-Vis spec outputs into a single data table and convert to absorption coefficients
Run this script first
User must: 
: IN WINDOWS EXPLORER
: -pull latest version of the code from github repo MMP-CDOM/JCU_lab (or relevent branch). See Daniel Moran for help with this if you need assistance accessing the repo
: -copy script to the working directory and add batch information to the script filename eg. "CDOM_1_processing_bCDOM-JCU_J25-0095.Rmd"
: -reveiw the received data for typos, missing data or other errors and then create .CSVs of the raw CDOM absorbance and the chemistry data (used to extract metadata and identify the MMP station names)
: -create "extra" folder in the working directory and move run notes, a backup of the raw data and any additional files to this folder.
: IN the R SCRIPT FOR THIS BATCH
: -reset R session (windows CTRL+SHIFT+F10)
: -change the wd
: -change the file string information in "pwd" used for generating filenames to reflect the actual parent folder for the wd. (update to pwd generally only will need to be done for each years' processing if you are not moving the data.)
N.B.
Event sampling data files may include a mix of files from AIMS and JCU labs (depending on the workflows utilised during the event sampling). However this script should only include files that have been received from the JCU lab - during 2024-25 processing this data was collated by the JCU lab and provided as seperate tabs in an excel sheet also containing the LIMS chemistry data outputs.
R for windows does not like '\' so you will need to replace all the '\' in the filepath with '/'

copy file path here:
R:\Lagoon_WQ\results\CDOM\2025-26 report\JCE\J26-0029 #location on RWQPP

---

# setup packages
```{r, include=FALSE}
rm(list=ls())

#library(dplyr)
#library(data.table)
#library(tidyr)
#library(ggplot2)
#library(plyr)
#library(zoo)
library(tidyverse)
library(readxl) #for reading in excel files (output from JCU lab)
library(data.table)

```


## Set the working directory
###MUST change '\' to '/' in path
```{r, include=FALSE}

#knitr::opts_knit$set(root.dir = "R:/Lagoon_WQ/results/CDOM/2025-26 report/WQR/CDOM-20251015_WQR331-347")
wd <- getwd() #relies on the default working directory based on the location of the script. so users MUST copy the script to the folder where the raw scans are located so this becomes the wd for the batch that is processing.
pwd<- dirname(getwd()) #used for creating file paths and other functions in this script

#setwd("R:/Lagoon_WQ/results/CDOM/2025-26 report/JCE/J26-0029")
#wd <- getwd()
#pwd<- "R:/Lagoon_WQ/results/CDOM/2025-26 report/JCE"
```


## Create some folders in the wd for saving outputs
```{r, include= FALSE}
getwd()

{dir.create(file.path(wd,"outputs"),
           showWarnings = FALSE)
dir.create(file.path(wd,"outputs","plots"),
           recursive = TRUE,
           showWarnings = FALSE)
dir.create(file.path(wd,"outputs","data"),
           recursive = TRUE,
           showWarnings = FALSE)
}

#{dir.create(file.path(wd,"outputs"))
#dir.create(file.path(wd,"outputs","plots"))
#dir.create(file.path(wd,"outputs","data"))
#}
```

## create lists of all files in the wd
```{r, include= FALSE}
#library(rlist)
{file_list <- list.files(wd, pattern="\\.xl", full.names=TRUE)
}
```


## Import the data from excel files 
```{r, include= FALSE}
#be aware that this step/chunk will likely require some manual handling if there are typos or slight changes to formatting coming from the JCU lab

#library(tidyverse)
#library(readxl) #for reading in excel files (output from salinometer)
#library(janitor)

CDOM_comp <- read_excel(file_list[2], sheet = 2, col_names = TRUE) #for excel files - we most likey will receive .xls or .xlsx rather than csv
#CDOM_comp <- read.csv(file_list[1], header =  TRUE) #for csv files

names(CDOM_comp)

# Find all columns that look like any variation of Milli-Q
milliq_cols <- names(CDOM_comp)[str_detect(
  names(CDOM_comp),
  regex("milli[[:space:]_-]*q", ignore_case = TRUE))
  ]

# Rename first and last Milli-Q columns
if (length(milliq_cols) >= 2) {
  CDOM_comp <- CDOM_comp  |> 
    dplyr::rename(
      MilliQ_start = all_of(milliq_cols[1]),
      MilliQ_end   = all_of(milliq_cols[length(milliq_cols)])
    )
} else {
  warning("Could not identify at least two Milli-Q columns")
}

names(CDOM_comp)

#rename wavelength column
CDOM_comp <- dplyr::rename(CDOM_comp, 'Wavelength_nm' = 'Wavelength nm.')

names(CDOM_comp)


metaheaders <- read_excel(file_list[1], n_max = 1, col_names =  TRUE) #check the deaders they are often across 2 lines from JCU LIMS output
#metaheaders <- metaheaders |> janitor::clean_names()
metaheaders <- names(metaheaders)
#metaheaders <- read.csv(file_list[2], nrows = 2, header =  FALSE)
#metaheaders = sapply(metaheaders, paste, collapse = "")
metaheaders

metadata <- read_excel(file_list[1], skip=2, col_names = metaheaders)
metadata <- metadata %>% select(c(1:5))
#metadata <- read.csv(file_list[2], skip=3, col.names = metaheaders, header = FALSE)
#metadata <- rename(metadata, short_name = sample_description)
names(metadata)
metadata <- dplyr::rename(metadata, station_name_depth = "Bottle ID for Sample Bottle")
metadata$station_name_depth
#str_sub(metadata$station_name_depth, 7, 6) <- "_" #add underscore between station and depth code if multiple peths are sampled
#metadata$station_name_depth
names(metadata)
metadata <- metadata %>% mutate(Sample = paste(metadata$Reference, "/", metadata$"Sample No.", sep = ""))
names(metadata)
metadata$Sample
metadata <- metadata %>% relocate(Sample, .after = "Sample No.")
names(metadata)
#metadata <- metadata %>% select(c(Event..:short_name))
#names(metadata)
metadata$Sample
#metadata$Sample <- str_replace(metadata$Sample, c("-"), c("_"))
metadata$Sample
metadata <- distinct(metadata)

metadata2 <- metadata %>% select(c(Sample, station_name_depth))


```

```{r, include= FALSE}
#only use this chunk if you need to handle rescans or duplicate scans
#add a row to metadata2 for the rescan of sample JCF442_D0 - including the rescan so the 2 scans can be assessed against each other

#names(CDOM_comp)
#names(metadata2)
#metadata2$station_name_depth
#metadata2 <- metadata2 |> add_row(Sample = "J25.0095.1.1", station_name_depth = "JCF442_D0_2", .before = 2)
#metadata2
```


### plot blank curves to look for drift - we are only plotting this to eyeball the control scans and ensure we are happy with the JCU output at a gross level - they only have start and end blank scans and the supplied data does not include timestamps or other analytical metadata so drift corrections are not practical

## 1st create a dataframe with milliQ blanks only
```{r, include= FALSE}

list <- names(CDOM_comp)  
batch <- str_remove(wd, pwd)
batch <- str_remove(batch, "/")
scan_list <- setdiff(list, "Wavelength_nm")
blank_list <- list[grep("illi",list)]
samples_list <- setdiff(list, blank_list)
samples_list <- setdiff(samples_list, "Wavelength_nm")

CDOM_long <- pivot_longer(CDOM_comp, cols = MilliQ_start:MilliQ_end, names_to = 'Sample', values_to = 'Absorbance', cols_vary = "fastest")
sapply(CDOM_long, class)
CDOM_long <- mutate(CDOM_long, Sample=factor(Sample, levels = scan_list)) 
#CDOM_long <- CDOM_long |> mutate(Sample=factor(Sample, levels = scan_list)) #as pipe
sapply(CDOM_long, class)
levels(CDOM_long$Sample)

#filter to show  half-nanometer increments only
filter_vals <- seq(250, 750, by=0.5)
names(CDOM_long)
CDOM_long <- filter(CDOM_long, Wavelength_nm %in% filter_vals)
CDOM_long$Wavelength_nm
rm(filter_vals)
#CDOM_long$Batch <- batch

#create df of the blanks 
CDOM_blanks <- filter(CDOM_long, Sample %in% blank_list)

#now remove the blank scans and replace Sample as JCU lab sample ID with station_name_depth
#CDOM_long2 <- filter(CDOM_long, Sample %in% samples_list)
CDOM_long <- merge(CDOM_long, metadata2, by= "Sample")
names(CDOM_long)
CDOM_long <- arrange(CDOM_long, Wavelength_nm)
names(CDOM_long)
CDOM_long <- filter(CDOM_long, Sample %in% samples_list)
CDOM_long <- CDOM_long |>  select(Wavelength_nm, Absorbance, station_name_depth)
CDOM_long <- dplyr::rename(CDOM_long, Sample = station_name_depth)
CDOM_long <- CDOM_long  |>  relocate(Sample)
names(CDOM_long)
typeof(CDOM_long$Absorbance)
CDOM_long$Sample <- factor(CDOM_long$Sample)
sapply(CDOM_long, class)
samples_list <- levels(CDOM_long$Sample)



```

## plot the data in CDOM_blanks, organise by samples, to look for drift
```{r, include= TRUE}
{#library(ggplot2)
driftplot <- ggplot(CDOM_blanks, aes(x = Wavelength_nm, y = Absorbance, colour = Sample)) + 
  geom_line(linewidth=0.1) +
  ylab('Absorbance') +
  xlab('Wavelength_nm') +
  scale_y_continuous(minor_breaks = NULL, breaks=seq(-0.02,0.02,0.01),limits=c(-0.02,0.02)) +
  scale_x_continuous(minor_breaks = NULL, breaks=seq(250,750,50), limits=c(250,750)) +
  theme_gray() 
driftplot
}

#save a copy of the driftplot as a .jpg
{
plotpath <- file.path(wd,"outputs","plots")
#batch <- str_remove(wd, pwd)
#batch <- str_remove(batch, "/")
batch <- basename(wd)
plotfilename <- paste(batch,"_driftplot.jpg",sep = "")
#ggsave(plotfilename, path=plotpath)
ggsave(filename = file.path(plotpath, plotfilename),
      width = 10,
      height = 6,
      dpi = 300)
}



```
#convert back to wide format and save a copy of the raw absorbance scan data. note no drift corrected data is generated - blank drift plots are only generated to allow for qualitative assessment
```{r, include= FLASE}
{
#CDOM_matrix <- spread(CDOM_long, key = Sample, value = Absorbance)
CDOM_matrix <- pivot_wider(CDOM_long, id_cols = Wavelength_nm, names_from = Sample, values_from = Absorbance)

## write matrix data table to file
#datasaveraw <- paste(wd, "/outputs/data/", batch, "_raw.csv", sep="")
datapath <- file.path(wd,"outputs","data")
datasaveraw <- file.path(datapath, paste0(batch,"_raw.csv"))
write.csv(CDOM_matrix,file=datasaveraw,row.names=F)
}

```

#run the conversion to ACDOM

#save the abrorbance coefficients

#produce and save plots for each sample

# re-write of code for calculating absorption coefficient etc (above) but using drift corrected data...
# CDOM data conversions - code from "CALCULATIONS" script by Christian Lomborg, adapted by Daniel Moran to batches of CDOM scans from Shimadzu UV-1900 UV-Vis spec...
## Outputs (for each sample):
## CDOM data conversion using "internal correction approach" to give absorbtion coefficient at each wavelength (Acdom). (see Lønborg & Álvarez-Salgado / Deep-Sea Research 85 (2014) 35-46)
## Factor 23.03 in calculating Acdom converts from decadic to natural logarithms and considers the cell path-length (10cm) (see Lønborg & Álvarez-Salgado / Deep-Sea Research 85 (2014) 3546)
## Note. if a different cell path legth is used (anything other than 10cm) than the factor will need to be adjusted. factor=2.303/path length in meters
## spectral slope (S). see C. A. Stedmon and S. Markager / Limnol. Oceanogr., 46(8), 2001, 2087-2093
## plots of fit between observed and modelled data (based on S) 
  
```{r, include= FLASE} 

rsq <- function(x, y) summary(lm(y~x))$r.squared

CDOM_conv <- list()
CDOM_conv2 <- list()
CDOM_conv3 <- list()

  for (f in samples_list) {
      dat <- filter(CDOM_long, Sample == f)
      dat$Sample  <-  factor(dat$Sample, levels = f)
      dat2 <- data.frame(Sample = factor(f))
      MeanAbs600_750 <- mean(subset(dat, Wavelength_nm >=600 & Wavelength_nm <=750)$Absorbance, na.rm=TRUE)
      dat2$MeanAbs600_750_raw <- MeanAbs600_750
      
      dat$Acdom  <-  23.03 * (dat$Absorbance - MeanAbs600_750)
      
      Acdom350  <-  dat$Acdom[dat$Wavelength_nm==350]
      dat$Acdom350  <-  Acdom350
      dat2$Acdom350  <-  Acdom350
      deltaLambda  <-  dat$Wavelength_nm - dat$Wavelength_nm[dat$Wavelength_nm==350]
      dat$deltaLambda <- deltaLambda
      Acdom443  <-  dat$Acdom[dat$Wavelength_nm==443]
      dat2$Acdom443  <-  Acdom443
      modeldat <- dat |> filter(Wavelength_nm >= 380, Wavelength_nm <= 680) #objective of model fitting is to represent absorbance of the visible spectra and generate fitted Acdom(443) so am reducing the fitting range to 380-680nm. this avoids noisier segment off the spectrum between 340-380 due to instrument artefacts (lamp changover). note the reference wavelength is stil 350nm
      
      #dat.nls <- nls(Acdom ~ Acdom350*exp(-S*deltaLambda) + K,
      #               data=modeldat, start=list(S=0.015, K = 0), control=nls.control(maxiter=1000)) 
      
      dat.nls <- nls(Acdom ~ Acdom350*exp(-S*deltaLambda),
                     data=modeldat, start=list(S=0.015), control=nls.control(maxiter=1000)) #using model without K. inner filter effects are accounted for in the conversion to Acdom already and the model without K seemed to provide a better representation of Acdom(443)
      
      summary(dat.nls)
      #dat2$S<-coef(dat.nls)
      dat2$S <- coef(dat.nls)[["S"]]
      #dat2$K <- coef(dat.nls)[["K"]] #continuing to exclude K

      xs <- seq(380,680,by=0.5) - dat$Wavelength_nm[dat$Wavelength_nm==350]
      newdata <- data.frame(deltaLambda=xs)
      fit <- predict(dat.nls, newdata=newdata)
      newdata <- cbind(newdata, fit)
      newdata$Sample  <-  factor(f)
      newdata$wavelength_nm <- newdata$deltaLambda + 350
      
      GoF_temp <- newdata
      data1 <- filter(dat, Wavelength_nm >= 380.0 & Wavelength_nm <= 680.0)
      GoF_temp$Acdom  <-  data1$Acdom
      r_squared <- rsq(GoF_temp$Acdom, GoF_temp$fit)
      
      plotpath <- file.path(wd,"outputs","plots")
      plotfilename <- paste(dat2$Sample,".jpg",sep = "")
      print(ggplot(dat, aes(y=Acdom, x=Wavelength_nm)) + geom_line()+
              geom_line(data=newdata, aes(y=fit, x=wavelength_nm), color='red')+
              #geom_point(data=newdata, aes(y=resid, x=wavelength_nm), color='blue', size=0.1)+
              #ggtitle(paste(dat2$Sample,': S=', sprintf("%.4f",dat2$S), ', ', 'R^2=', sprintf("%.4f",r_squared), ', ', 'K=', sprintf("%.3f",dat2$K)))+
              ggtitle(paste(dat2$Sample,': S=',dat2$S, ', ', 'R^2=', r_squared))+
              scale_y_continuous(expression(A[cdom]))+
              scale_x_continuous(expression(Wavelength (nm))))
      #ggsave(plotfilename, path=plotpath)
      ggsave(filename = file.path(plotpath, plotfilename),
            width = 10,
            height = 6,
            dpi = 300)
      
      CDOM_conv <- rbind(CDOM_conv, dat) 
      dat2 <- as.data.frame(dat2,row.names=seq())
      CDOM_conv2 <- rbind(CDOM_conv2, dat2) 
      CDOM_conv3 <- rbind(CDOM_conv3, newdata) 
      
      rm(dat)
      rm(dat2)
      rm(newdata)
      rm(modeldat)
      rm(dat.nls)
      rm(fit)
      rm(xs)
      rm(MeanAbs600_750)
      rm(Acdom350)
      rm(deltaLambda)
      rm(Acdom443)
      rm(GoF_temp)
      rm(r_squared)
      rm(data1)
    }
  
```  


## create an object containing the new directory and name of compiled data to be saved
```{r, include= FLASE}
  {
    datasave2 <- file.path(datapath, paste0(batch, "_factors.csv"))
    datasave4 <- file.path(datapath, paste0(batch, "_Acdom.csv"))
    
    ## write data table to file
    write.csv(CDOM_conv2,file=datasave2, row.names=F)
    
    ## remove the deltaLambda and Abs. column from the compiled data
    CDOM_conv4 <- CDOM_conv
    CDOM_conv4$deltaLambda <- NULL
    CDOM_conv4$Abs_corr <- NULL
    
    ## create a matrix for CDOM_conv data (i.e. convert to 'wide' format)
    #library(tidyr)
    ACDOM_matrix <- pivot_wider(CDOM_conv4, id_cols = Wavelength_nm, names_from = Sample, values_from = Acdom)
    ## write matrix data to file
    write.csv(ACDOM_matrix,file=datasave4, row.names=F) 
  }
```  


##calculate Rsquared for GoF (loop)
```{r, include= FLASE}
dat_GoF <- CDOM_conv3
dat_GoF$deltaLambda <- NULL
temp <- filter(CDOM_conv4, Wavelength_nm >= 380.0 & Wavelength_nm <= 680.0)
dat_GoF$Acdom <- temp$Acdom
dat_GoF <- dat_GoF[c("Sample", "wavelength_nm", "Acdom", "fit")]
temp <- NULL
rsq <- function(x, y) summary(lm(y~x))$r.squared

# create a dataframe for the merged data
datR2 <- data.frame()
# and append the data to this dataframe
for (z in samples_list) {
    GoF_temp <- filter(dat_GoF, Sample==z)
    dat <- data.frame(Sample = z)
    r_squared <- rsq(GoF_temp$Acdom, GoF_temp$fit)
    dat$r_squared <- r_squared
    datR2 <- rbind(datR2, dat)
    }


#rm(dat)
#rm(GoF_temp)
#rm(r_squared)

#print datR2
#datasaveR2 <- paste("outputs/data/",(gsub(pwd,"",wd)),"_GoF",".csv", sep="")
#write.csv(datR2,file=datasaveR2,row.names=F)
```

##calculate CDOM_443 from modeled data
```{r, include= FLASE}
#library(data.table)
CDOM_conv3$wavelength_nm <- CDOM_conv3$deltaLambda + 350
{
  model_443 <- filter(CDOM_conv3, wavelength_nm == 443.0)
  model_443 <- group_by(model_443, Sample)
  model_443$model_443 <- model_443$fit
  model_443$wavelength_nm <- NULL
  model_443$fit <- NULL
  model_443$deltaLambda <- NULL
  names(model_443)
  names(datR2)
  #print CDOM_443
  model_443 <- model_443 |> full_join(datR2)
  model_443 <- model_443 |> full_join(CDOM_conv2)
  names(model_443)
  model_443$MeanAbs600_750_raw <- NULL
  model_443$Acdom350 <- NULL
  model_443$S <- NULL
  names(model_443)
  #datasavemodel443 <- paste(wd, "/outputs/data/", batch, "_model443",".csv", sep="")
  datasavemodel443 <- file.path(datapath, paste0(batch,"_model443.csv"))
  
  write.csv(model_443,file=datasavemodel443,row.names=F)
}

```