---
title: "CDOM_2_merge_files"
output: html_document
---

## 
# before using this script you must have already run CDOM processing script on individual analytical batches of CDOM data auto-exported from the AIMS WQ Shimadzu UV-1900 UV-Vis spectrophotometer
# input required to the current script are the entire complement of processed CDOM data batches for a water year, where each scan in each analytical batch has been cleaned, checked for drift and corrections applied
# before collated the outputs all scans (plots output from processing script) must be inspected and pass initial QC
##

Daniel Moran
AIMS
update 06/07/21 (Alex Macadam)
update 31/05/2023 ?
update 12/06/2025 import to github MMP-CDOM repo
update: 17/06/2025 moved this script to github repo MMP-CDOM/main and renamed to remove now redundant version control (no longer required with move to github).
update: 17/06/2025 reformatted to .Rmd 

Combine model_443 and Rsquared outputs from each batch into a single dataframe and save as a .csv file
Note that R does not like '\' so you will need to replace all the '\' in the filepath with '/'
Note that the script collates data from any file with "model443_drift_corr" in the filename, from all subdirectories. If there are any precious processing batches in 
Sub-directories make sure these are hidden by zipping


# setup packages
```{r, include=FALSE}
rm(list=ls())

library(tidyverse)

```


#set the wd
```{r, include=FALSE}

wd <- getwd() #relies on the default working directory based on the location of the script. so users MUST copy the script to the folder where the batch folders are located so this becomes the wd.

```


Collate and print the model_443 Acdom values and the Rsquared values for all samples
```{r, include=FALSE}

# create list of all files in the wd with model443 and Rsquared data fields
file_list <- list.files(pattern="model443_drift_corr.csv", full.names=FALSE, recursive = TRUE) # recursive = TRUE allows list.files function to look in all subdirectories 
file_list #check that the listed files matches your expectations!
## import all the model443 .CSVs in the wd to a single dataframe
## create a "Filename" column containing the file name associated with each row 

# create a dataframe for the merged data
CDOM_443_all <- data.frame()

# now loop to append all the data from the different csv files to this dataframe
for (x in file_list){
    temp_dataset <-ldply(x, read.csv, header=TRUE, skip=0, sep=',',col.names=c('Sample','model_443','r_squared'))
    CDOM_443_all <- rbind(CDOM_443_all, temp_dataset)
    rm(temp_dataset)
  }
View(CDOM_443_all)

#order by Sample name
sapply(CDOM_443_all, class)
CDOM_443_all$model_443 <- as.numeric(CDOM_443_all$model_443)
CDOM_443_all$Sample <- as.character(CDOM_443_all$Sample)
CDOM_443_all$r_squared <- as.numeric(CDOM_443_all$r_squared)
CDOM_443_all <- CDOM_443_all[order(CDOM_443_all$Sample),]
View(CDOM_443_all)

# if there are non-target samples from some of the analytical batches then remove them.
wd #to confirm the target station family
CDOM_443_all <- CDOM_443_all |> filter(str_detect(basename(wd)))
View(CDOM_443_all)

#print the data
#path <- file.path(wd)
write.csv(CDOM_443_all,file="2024-25_JCZ_CDOM443.csv",row.names=F)

```


